\documentclass{article}
\usepackage[utf8]{inputenc}
\begin{document}

John, Paul, Ringo, and George all decided to go on a yellow submarine one day.
They arrive at the harbor with packed peanut butter and jelly sandwiches,
their submarine licenses, and a sense of adventure.
They all climb in, ready to explore the murky waters of the English Channel.
However, they know something that most seafaring people don’t.
There is a secret place in the deep depths that contains a teeming environment
filled with octopi, merpeople, and brightly colored coral.
The quad submerges into the icy waters. Ringo, as he is usually always hungry,
begins munching on his sandwich as Paul and John begin bickering about how to
get to the secret location… \\

The four were submerging deeper into the water rapidly without realizing that
the light was starting to fade away.\\

Ringo was too busy eating his peanut butter and jelly sandwiches that he was
unaware of where their submarine had taken them.\\

George had been reading \textit{The Catcher in the Rye} this entire time and was
also unaware of how much time had even passed by.\\

And well, John and Paul were just too busy trying to understand the map that they
also became unaware of the strange, dark place they had now entered. \\

Instantly, the four dropped their sandwiches, books, and maps and began to stare
at the darkness that appeared outside the windows of the submarine. In a matter
of seconds, Ringo and George suggested that they surface back up before coming
across some dangerous monster. However, John and Paul were determined to find this
secret location.\\

Choose the surface branch if you agree with Ringo and George that they should
head back up, or choose the location branch if you agree with John and Paul that
they should continue with their adventure …\\

John and Paul were able to convince Ringo by bribing him and promising that they
would give him as many peanut butter and jelly sandwiches he wanted once they
returned from their trip. And well, George’s opinion of returning back home was
not taken into account since majority rules. \\

So, off they were headed to find the so-called secret location. They submerged
deeper into the darkness but something strange began happening. \\

Their submarine was being moved involuntarily from side to side. The movement
started slow at first but then became more violent. All four were scared for
their lives. John was able to point the dim lights of the submarine at whatever
was out there, and once they were able to identify what it was all all four let
out loud screams. \\

They were huge octopi tentacles! These octopi were not normal octopi. They were
ferocious and ready to kill whatever came near the entrance of the place they guarded.\\

They had come so far and were right at the entrance of the secret place but were
not able to enter unless they wanted to die. Without even discussing what to do
next, all four realized that they were going to have to retrieve and return back
to surface before risking their lives. 

\end{document}
